Himalayan Expeditions Success Analysis 

### 2024-04-13 paper/paper.qmd
Data section updated

---
title: "Himalayan Expeditions Success Analysis "
subtitle: "Analysis using data from XXX leveraging Bayesian Logistic Regression"
author: Kaavya Kalani
thanks: "Code and data supporting this analysis is available at: https://github.com/kaavyakalani26/himalayan-expeditions-analysis"
date: today
date-format: long
abstract: "Abstract"
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

@@

## Analysis Dataset
The analysis data is from XXXX. This is how it was collected.

A person becomes an entry in this dataset if XXX. (Measurement)

The data from datasets for XXX are combined to form our anaysis dataset. Among the overall range of variables available, we chose XXX to be included in our analysis dataset.

- Describe the variables

Out of these, we will be using XXX in our model as the independent variables and XXX as the dependent variable.

>>>>

---
title: "Himalayan Expeditions Success Analysis "
subtitle: "Analysis using data from Himalayan expeditions from 1905 through Spring 2019 leveraging Bayesian Logistic Regression"
author: Kaavya Kalani
thanks: "Code and data supporting this analysis is available at: https://github.com/kaavyakalani26/himalayan-expeditions-analysis"
date: today
date-format: long
abstract: "Abstract"
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

@@

## Analysis Dataset
The raw datasets were obtained from Alex Cookson's datasets (link). I chose the ones cleaned for Himalayan expeditions. Alex got his datasets from The Himalayan Database (link).

The Himalayan Database is a compilation of records for all expeditions that have climbed in the Nepal Himalaya. The database is based on the expedition archives of Elizabeth Hawley, a longtime journalist based in Kathmandu, and it is supplemented by information gathered from books, alpine journals and correspondence with Himalayan climbers.

The original database currently covers all expeditions from 1905 through Spring-Summer 2023 to the most significant mountaineering peaks in Nepal. Also included are expeditions to both sides of border peaks such as Everest, Cho Oyu, Makalu and Kangchenjunga as well as to some smaller border peaks. Data on expeditions to trekking peaks are included for early attempts, first ascents and major accidents. The updates to this database are published bi-annually.

My dataset derived from Alex's contains the entries from 1905 through Spring 2019.

The three datasets I considered included information about all peaks, all expeditions on those peaks and all members on those expeditions. The data from these three datasets are combined to form our analysis dataset.

A person becomes an entry in my analysis dataset if, between 1905 and Spring 2019, they attempted to climb any one of the many Himalayan peaks in Nepal. It also included expeditions to both sides of border peaks as mentioned before.

Among the overall range of variables available, we chose the following to be included in our analysis dataset.

- `Height of the peak` in metres for the peak the person in the current entry is on an expedition for
- `Seasons` is the season the expedition is in. This takes on either of the 4 values: Autumn, Spring, Winter, Summer.
- `Sex` is the sex reported by the expedition member and it is either male or female.
- `Age` is the age of the expedition member at the time of the expedition. Depending on the best available data, this could be as of the summit date, the date of death, or the date of arrival at basecamp.
- `Success`represents whether the person was successful in summitting the goal peak.
- `Solo` represents whether the person attempted a solo ascent.
- `Died` represents whether the person died during the expedition.

Out of these, we will be using `height of the peak`, `seasons`, `sex`, `age` and `solo` in our model as the independent variables and `success` as the dependent variable.
